IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-05 paper/formal.tex
nit

Given an information flow control language, we can now define non-interference.
Intuitively, we want to make statements about the attacker's observational
power at some security level |l|.  This is done by defining an equivalence
relation called |l|-equivalence on configurations: an attacker should
not be able to distinguish two configuration that are |l|-equivalent.
%
Since our erasure function captures what an attacker can or cannot observe, we simply define this
equivalence as the syntactic-equivalence of erased configurations~\cite{stefan:addressing-covert}.
%
\begin{definition}[|l|-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    |memberf (c, c') C| are considered $l$-equivalent, written as |c ~= c'|,
    if |erase l c = erase il c'|.
\end{definition}
%

@@

In general, however, non-interference will not hold for an arbitrary scheduler |alpha|.
%
For example, |specLang alpha targetLang| with a scheduler that inspects a
sensitive tasks current state when deciding which task to schedule next
will in general break non-interference~\cite{russo2006securing,BartheRRS07}.
%
%In Section~\toref{} we detail the preceise scheduler for which our
%specification language is TSNI.
%

>>>>

Given an information flow control language, we can now define non-interference.
Intuitively, we want to make statements about the attacker's observational
power at some security level |l|.  This is done by defining an equivalence
relation called |l|-equivalence on configurations: an attacker should
not be able to distinguish two configuration that are |l|-equivalent.
%
Since our erasure function captures what an attacker can or cannot observe, we simply define this
equivalence as the syntactic-equivalence of erased configurations~\cite{stefan:addressing-covert}.
%
\begin{definition}[|l|-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    |memberf (c, c') C| are considered $l$-equivalent, written as |c ~= c'|,
    if |erase l c = erase l c'|.
\end{definition}
%

@@

In general, however, non-interference will not hold for an arbitrary scheduler |alpha|.
%
For example, |specLang alpha targetLang| with a scheduler that inspects a
sensitive task's current state when deciding which task to schedule next
will in general break non-interference~\cite{russo2006securing,BartheRRS07}.
%
%In Section~\toref{} we detail the preceise scheduler for which our
%specification language is TSNI.
%
